The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-02-08 repeater-vladata.tex
new cumulative plot
energy dist model makes sense

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}). The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band. If those bursts only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties. We proceed under this assumption here and discuss caveats later.

The \frb\ burst energy distribution is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$). All bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.

We visualize perform a simple modeling the burst energy distribution distribution and cumulative distribution in Figure \ref{fig:ed}.
The energy distribution powerlaw index is --0.5, while its cumulative energy distribution powerlaw index is --0.6.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{energy_disn}
\caption{The \frb\ burst energy distribution and cumulative distributino with powerlaw fits \label{fig:ed}}
\end{center}
\end{figure}

>>>>

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}). Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within the 2.5 to 3.5~GHz band. Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties. We proceed under this assumption here and discuss caveats later.

The \frb\ burst energy distribution (Figure \ref{fig:ed}) is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$). We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\proptoE^{\alpha}$. Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.4}_{-0.6}$. This is equivalent to a differential energy distribution, $dN/dE \propto E^{-1.6}$. Note that all VLA bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{energy_disn}
\caption{Dots and solid line show the  \frb\ burst energy cumulative distribution. The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$. The 95\% bounds on the best-fit powerlaw index is $\alpha=-1.6^{+0.4}_{-0.6}$. \label{fig:ed}}
\end{center}
\end{figure}
